---
title: "Periop Unit Report"
author: "Tom Lawton"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        intermediates_dir=Sys.getenv("TEMP"),
                        output_dir="../Rmd Outputs/") })
output:
  word_document:
    reference_docx: template.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(crop = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = FALSE)
knitr::opts_chunk$set(fig.height=4)
knitr::opts_chunk$set(fig.width=6.5)
knitr::opts_chunk$set(dpi=200)
##knitr::opts_chunk$set(eval = FALSE)
#knitr::opts_chunk$set(dev='win.metafile')
##options(tinytex.verbose = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(lubridate)
library(stringr)

loadnameRDS<-function(filename) {
  dfname<-gsub(basename(filename),pattern=".rds$",replacement="")
  temp<-readRDS(filename)
  if (grepl("attrib",dfname)) {
    temp<-temp %>% 
      mutate(key=str_replace_all(key,c(
        "21CC_Elective_OTD_Cancellations" = "Cancellations from Wd21",
        "ICU_Elective_OTD_Cancellations" = "Cancellations from HDU/ICU",
        "Periop_Elective_OTD_Cancellations" = "Cancellations from Periop",
        "Elective_OTD_Cancellations" = "Elective OTD Cancellations", ## must be last or matches the earlier ones
        "ICU_Admissions_12H_Delayed" = "ICU Admissions delayed 12hr",
        "21CC_Admissions_12H_Delayed" = "Wd21 Admissions delayed 12hr",
        "Periop_Admissions_12H_Delayed" = "Periop Admissions delayed 12hr",
        "CC_Discharges_24H_Delayed" = "Ward Discharges delayed 24hr"
      )))
  }
  assign(dfname,temp,envir=.GlobalEnv)
}
filenames <- list.files("../Model Outputs/",pattern="^(1|7).*rds",full.names=TRUE)
invisible(lapply(filenames,loadnameRDS))



```

## Explanation of graphs

### Beds
* red/blue dots - individual runs
* blue line - average across all runs
* grey area - roughly 95% confidence interval

### Cancellations
* Elective_OTD_Cancellations is the total for a year
* Within that are listed "special" cancellations - eg due to lack of beds on ICU, 21CC (monitored beds on 21), Periop unit
* Special cancellations show the kind of bed the patient was originally looking for, though they won't have been cancelled if they could have gone elsewhere (eg Periop patient would have gone to ICU if there had been a bed)

### Delays
* Number of patients severely delayed getting out of a critical care bed (includes 21 monitored), or getting into a critical care bed and its type

## Infinite beds - ie capacity testing (scenario 7)

### Occupancy of periop unit:
```{r}
start_date<-as.POSIXct("2019-10-01",origin="1970-01-01 00:00.00 UTC")
end_date<-as.POSIXct("2021-03-31",origin="1970-01-01 00:00.00 UTC")
resources2<-filter(`7-resources`,resource=="Periop")
resources2$time<-as.POSIXct(resources2$time,origin="1970-01-01 00:00.00 UTC")
resources2$rdate<-round_date(resources2$time,unit="day")
resources2$rwdate<-round_date(resources2$time,unit="week")

print(ggplot(resources2,aes(x=rdate,y=server,color=replication)) +
        geom_point(alpha=0.1,shape=16) +
        scale_color_gradient(low="blue", high="red",guide=FALSE) +
        stat_summary(aes(x=rwdate,y=server),fun.data="mean_sdl",geom="smooth",se=TRUE,size=2)  +
        xlim(start_date,end_date)  +
        labs(x="Date",y="Beds") + theme_bw(base_size=12)+
        ggtitle("Scenario 7 Periop Occupancy (unlimited)"))

```

## Baseline scenario
ie present hospital

### Cancellations

```{r}
start_date<-as.POSIXct("2020-03-31",origin="1970-01-01 00:00.00 UTC")
end_date<-as.POSIXct("2021-03-31",origin="1970-01-01 00:00.00 UTC")
`max_attribs_start`<-`1-attribs` %>%
  filter(time<start_date) %>%
  group_by(key,replication) %>%
  summarise(value=max(value))
`max_attribs_end`<-`1-attribs` %>%
  filter(time<end_date) %>%
  group_by(key,replication) %>%
  summarise(value=max(value))
t<-`max_attribs_end` %>% 
  arrange(replication) %>% 
  pivot_wider(names_from="key",values_from="value",values_fill=list(value=0))
t2<-`max_attribs_start` %>% 
  arrange(replication) %>% 
  pivot_wider(names_from="key",values_from="value",values_fill=list(value=0))
t3<-t-t2
t3$replication<-t$replication
max_attribs<-pivot_longer(t3,-replication,names_to="key",values_to="value")
max_attribs$Scenario<-"Baseline"
## Draw data off for summary plot later
summary_max_attribs<-max_attribs
plot_max_attribs<-filter(`max_attribs`,grepl("Cancellations",key))
plot_max_attribs$key<-with(plot_max_attribs,reorder(key,-value)) ## ensure legend is reordered as well as bars
print(ggplot(plot_max_attribs,aes(x=key,y=value,fill=key)) +
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6) +
        theme_bw(base_size=12)+
        theme(axis.text.x=element_blank(),axis.title.x=element_blank(),axis.title.y=element_blank())+
        ggtitle("Baseline Cancellations") )

```

### Critical Care Delays

```{r}
plot_max_attribs<-filter(`max_attribs`,grepl("delayed",key))
plot_max_attribs$key<-with(plot_max_attribs,reorder(key,-value))
print(ggplot(plot_max_attribs,aes(x=reorder(key,-value),y=value,fill=key)) +
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6) +
        theme_bw(base_size=12)+
        theme(axis.text.x=element_blank(),axis.title.x=element_blank(),axis.title.y=element_blank())+
        ggtitle("Baseline Critical Care Delays") )
```

### Occupancy (total)

``` {r}
start_date<-as.POSIXct("2019-10-01",origin="1970-01-01 00:00.00 UTC")
end_date<-as.POSIXct("2021-03-31",origin="1970-01-01 00:00.00 UTC")
resources2<-dplyr::filter(`1-resources`,resource=="bed")
resources2$time<-as.POSIXct(resources2$time,origin="1970-01-01 00:00.00 UTC")

##Take a sample so that ggplot can do this in under an hour!
resources_samp<-resources2[sample(nrow(resources2),50000),]
resources_samp$rdate<-round_date(resources_samp$time,unit="day")
resources_samp$rwdate<-round_date(resources_samp$time,unit="week")

# Daily everything with summary graph
# ggplot(resources_samp,aes(x=rdate,y=server,color=replication)) + geom_point(alpha=0.1,shape=16) + scale_color_gradient(low="blue", high="red") + stat_summary(fun.data="mean_sdl",geom="smooth",se=TRUE)  + xlim(start_date,end_date) + ylim(400,700)


##Daily points with weekly data for summary graph:
#resources4$rwdate<-round_date(resources4$time,unit="week")
 print(ggplot(resources_samp,aes(x=rdate,y=server,color=replication)) +
         geom_point(alpha=0.1,shape=16) +
         scale_color_gradient(low="blue", high="red",guide=FALSE) +
         stat_summary(aes(x=rwdate,y=server),fun.data="mean_sdl",geom="smooth",se=TRUE)  +
         xlim(start_date,end_date) +
         ylim(400,700) +labs(x="Date",y="Beds") +
         theme_bw(base_size=12)+
        ggtitle("Baseline whole-hospital occupancy") )

```

## Scenario 7b
Periop unit with 6 beds, all extra to hospital

### Cancellations

```{r}
## Set up data by only considering events between these dates
start_date<-as.POSIXct("2020-03-31",origin="1970-01-01 00:00.00 UTC")
end_date<-as.POSIXct("2021-03-31",origin="1970-01-01 00:00.00 UTC")
`max_attribs_start`<-`7b-attribs` %>%
  filter(time<start_date) %>%
  group_by(key,replication) %>%
  summarise(value=max(value))
`max_attribs_end`<-`7b-attribs` %>%
  filter(time<end_date) %>%
  group_by(key,replication) %>%
  summarise(value=max(value))
t<-`max_attribs_end` %>% 
  arrange(replication) %>% 
  pivot_wider(names_from="key",values_from="value",values_fill=list(value=0))
t2<-`max_attribs_start` %>% 
  arrange(replication) %>% 
  pivot_wider(names_from="key",values_from="value",values_fill=list(value=0))
t.diff<-setdiff(colnames(t),colnames(t2)) ##may be some missing columns where values were all zero
t2[,c(as.character(t.diff))]<-0
t3<-t-t2
t3$replication<-t$replication
max_attribs<-pivot_longer(t3,-replication,names_to="key",values_to="value")
max_attribs$Scenario<-"7b"
## Draw data off for summary plot later
summary_max_attribs<-bind_rows(summary_max_attribs,max_attribs)

## Cancellations plot
plot_max_attribs<-filter(`max_attribs`,grepl("Cancellations",key))
plot_max_attribs$key<-with(plot_max_attribs,reorder(key,-value))
print(ggplot(plot_max_attribs,aes(x=reorder(key,-value),y=value,fill=key)) +
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6) +
        theme_bw(base_size=12)+
        theme(axis.text.x=element_blank(),axis.title.x=element_blank(),axis.title.y=element_blank())+
        ggtitle("Scenario 7b Cancellations") )

```

### Critical Care Delays

```{r}
plot_max_attribs<-filter(`max_attribs`,grepl("delayed",key))
plot_max_attribs$key<-with(plot_max_attribs,reorder(key,-value)) 
print(ggplot(plot_max_attribs,aes(x=reorder(key,-value),y=value,fill=key)) +
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6) +
        theme_bw(base_size=12)+
        theme(axis.text.x=element_blank(),axis.title.x=element_blank(),axis.title.y=element_blank())+
        ggtitle("Scenario 7b Critical Care Delays") )
```

### Use of Periop Unit

```{r}
resources2<-filter(`7b-resources`,resource=="Periop")
resources2$time<-as.POSIXct(resources2$time,origin="1970-01-01 00:00.00 UTC")
resources2$rdate<-round_date(resources2$time,unit="day")
resources2$rwdate<-round_date(resources2$time,unit="week")

print(ggplot(resources2,aes(x=rdate,y=server,color=replication)) +
        geom_point(alpha=0.1,shape=16) +
        scale_color_gradient(low="blue", high="red",guide=FALSE) +
        stat_summary(aes(x=rwdate,y=server),fun.data="mean_sdl",geom="smooth",se=TRUE,size=2)  +
        xlim(start_date,end_date)  +
        labs(x="Date",y="Beds") + theme_bw(base_size=12)+
        ggtitle("Scenario 7b Periop Occupancy (6 beds)"))
```

## Scenario 7c
Periop unit with 8 beds, all extra to hospital

### Cancellations

```{r}
## Set up data by only considering events between these dates
start_date<-as.POSIXct("2020-03-31",origin="1970-01-01 00:00.00 UTC")
end_date<-as.POSIXct("2021-03-31",origin="1970-01-01 00:00.00 UTC")
`max_attribs_start`<-`7c-attribs` %>%
  filter(time<start_date) %>%
  group_by(key,replication) %>%
  summarise(value=max(value))
`max_attribs_end`<-`7c-attribs` %>%
  filter(time<end_date) %>%
  group_by(key,replication) %>%
  summarise(value=max(value))
t<-`max_attribs_end` %>% 
  arrange(replication) %>% 
  pivot_wider(names_from="key",values_from="value",values_fill=list(value=0))
t2<-`max_attribs_start` %>% 
  arrange(replication) %>% 
  pivot_wider(names_from="key",values_from="value",values_fill=list(value=0))
t.diff<-setdiff(colnames(t),colnames(t2)) ##may be some missing columns where values were all zero
t2[,c(as.character(t.diff))]<-0
t3<-t-t2
t3$replication<-t$replication
max_attribs<-pivot_longer(t3,-replication,names_to="key",values_to="value")
max_attribs$Scenario<-"7c"
## Draw data off for summary plot later
summary_max_attribs<-bind_rows(summary_max_attribs,max_attribs)

## Cancellations plot
plot_max_attribs<-filter(`max_attribs`,grepl("Cancellations",key))
plot_max_attribs$key<-with(plot_max_attribs,reorder(key,-value)) 
print(ggplot(plot_max_attribs,aes(x=reorder(key,-value),y=value,fill=key)) +
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6) +
        theme_bw(base_size=12)+
        theme(axis.text.x=element_blank(),axis.title.x=element_blank(),axis.title.y=element_blank())+
        ggtitle("Scenario 7c Cancellations") )

```

### Critical Care Delays

```{r}
plot_max_attribs<-filter(`max_attribs`,grepl("delayed",key))
plot_max_attribs$key<-with(plot_max_attribs,reorder(key,-value)) 
print(ggplot(plot_max_attribs,aes(x=reorder(key,-value),y=value,fill=key)) +
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6) +
        theme_bw(base_size=12)+
        theme(axis.text.x=element_blank(),axis.title.x=element_blank(),axis.title.y=element_blank())+
        ggtitle("Scenario 7c Critical Care Delays") )
```

### Use of Periop Unit

```{r}
resources2<-filter(`7c-resources`,resource=="Periop")
resources2$time<-as.POSIXct(resources2$time,origin="1970-01-01 00:00.00 UTC")
resources2$rdate<-round_date(resources2$time,unit="day")
resources2$rwdate<-round_date(resources2$time,unit="week")

print(ggplot(resources2,aes(x=rdate,y=server,color=replication)) +
        geom_point(alpha=0.1,shape=16) +
        scale_color_gradient(low="blue", high="red",guide=FALSE) +
        stat_summary(aes(x=rwdate,y=server),fun.data="mean_sdl",geom="smooth",se=TRUE,size=2)  +
        xlim(start_date,end_date)  +
        labs(x="Date",y="Beds") + theme_bw(base_size=12)+
        ggtitle("Scenario 7c Periop Occupancy (8 beds)"))

```

## Scenario 7d
Periop unit with 8 beds, taken from Wd 21 (4 monitored, 4 unmonitored)

### Cancellations

```{r}
## Set up data by only considering events between these dates
start_date<-as.POSIXct("2020-03-31",origin="1970-01-01 00:00.00 UTC")
end_date<-as.POSIXct("2021-03-31",origin="1970-01-01 00:00.00 UTC")
`max_attribs_start`<-`7d-attribs` %>%
  filter(time<start_date) %>%
  group_by(key,replication) %>%
  summarise(value=max(value))
`max_attribs_end`<-`7d-attribs` %>%
  filter(time<end_date) %>%
  group_by(key,replication) %>%
  summarise(value=max(value))
t<-`max_attribs_end` %>% 
  arrange(replication) %>% 
  pivot_wider(names_from="key",values_from="value",values_fill=list(value=0))
t2<-`max_attribs_start` %>% 
  arrange(replication) %>% 
  pivot_wider(names_from="key",values_from="value",values_fill=list(value=0))
t.diff<-setdiff(colnames(t),colnames(t2)) ##may be some missing columns where values were all zero
t2[,c(as.character(t.diff))]<-0
t3<-t-t2
t3$replication<-t$replication
max_attribs<-pivot_longer(t3,-replication,names_to="key",values_to="value")
max_attribs$Scenario<-"7d"
## Draw data off for summary plot later
summary_max_attribs<-bind_rows(summary_max_attribs,max_attribs)

## Cancellations plot
plot_max_attribs<-filter(`max_attribs`,grepl("Cancellations",key))
plot_max_attribs$key<-with(plot_max_attribs,reorder(key,-value)) 
print(ggplot(plot_max_attribs,aes(x=reorder(key,-value),y=value,fill=key)) +
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6) +
        theme_bw(base_size=12)+
        theme(axis.text.x=element_blank(),axis.title.x=element_blank(),axis.title.y=element_blank())+
        ggtitle("Scenario 7d Cancellations") )

```

### Critical Care Delays

```{r}
plot_max_attribs<-filter(`max_attribs`,grepl("delayed",key))
plot_max_attribs$key<-with(plot_max_attribs,reorder(key,-value)) 
print(ggplot(plot_max_attribs,aes(x=reorder(key,-value),y=value,fill=key)) +
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6) +
        theme_bw(base_size=12)+
        theme(axis.text.x=element_blank(),axis.title.x=element_blank(),axis.title.y=element_blank())+
        ggtitle("Scenario 7d Critical Care Delays") )
```

## Scenario 7e
Periop unit with 8 beds, taken from Wd 21 (4 normal beds), 18 (2 beds), and 2 new created

### Cancellations

```{r}
## Set up data by only considering events between these dates
start_date<-as.POSIXct("2020-03-31",origin="1970-01-01 00:00.00 UTC")
end_date<-as.POSIXct("2021-03-31",origin="1970-01-01 00:00.00 UTC")
`max_attribs_start`<-`7e-attribs` %>%
  filter(time<start_date) %>%
  group_by(key,replication) %>%
  summarise(value=max(value))
`max_attribs_end`<-`7e-attribs` %>%
  filter(time<end_date) %>%
  group_by(key,replication) %>%
  summarise(value=max(value))
t<-`max_attribs_end` %>% 
  arrange(replication) %>% 
  pivot_wider(names_from="key",values_from="value",values_fill=list(value=0))
t2<-`max_attribs_start` %>% 
  arrange(replication) %>% 
  pivot_wider(names_from="key",values_from="value",values_fill=list(value=0))
t.diff<-setdiff(colnames(t),colnames(t2)) ##may be some missing columns where values were all zero
t2[,c(as.character(t.diff))]<-0
t3<-t-t2
t3$replication<-t$replication
max_attribs<-pivot_longer(t3,-replication,names_to="key",values_to="value")
max_attribs$Scenario<-"7e"
## Draw data off for summary plot later
summary_max_attribs<-bind_rows(summary_max_attribs,max_attribs)

## Cancellations plot
plot_max_attribs<-filter(`max_attribs`,grepl("Cancellations",key))
plot_max_attribs$key<-with(plot_max_attribs,reorder(key,-value)) 
print(ggplot(plot_max_attribs,aes(x=reorder(key,-value),y=value,fill=key)) +
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6) +
        theme_bw(base_size=12)+
        theme(axis.text.x=element_blank(),axis.title.x=element_blank(),axis.title.y=element_blank())+
        ggtitle("Scenario 7e Cancellations") )

```

### Critical Care Delays

```{r}
plot_max_attribs<-filter(`max_attribs`,grepl("delayed",key))
plot_max_attribs$key<-with(plot_max_attribs,reorder(key,-value)) 
print(ggplot(plot_max_attribs,aes(x=reorder(key,-value),y=value,fill=key)) +
        geom_boxplot() +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6) +
        theme_bw(base_size=12)+
        theme(axis.text.x=element_blank(),axis.title.x=element_blank(),axis.title.y=element_blank())+
        ggtitle("Scenario 7e Critical Care Delays") )
```

## Summary

### Scenarios
* **Baseline** - Hospital as at present
* **7** - Periop unit, infinite size (used only for capacity estimation, unrealistic)
* **7b** - Periop unit, 6 beds (all extra)
* **7c** - Periop unit, 8 beds (all extra)
* **7d** - Periop unit, 8 beds (taken from Wd21 - 4 monitored, 4 unmonitored)
* **7e** - Periop unit, 8 beds (4 unmonitored taken from Wd21, 2 from Wd18)

### On-the-day Cancellations
```{r}
plot_max_attribs<-filter(`summary_max_attribs`,grepl("OTD",key))
#plot_max_attribs$key<-with(plot_max_attribs,reorder(key)) 
print(ggplot(plot_max_attribs,aes(x=Scenario,y=value,fill=Scenario)) +
        geom_boxplot(show.legend=FALSE) +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6,show.legend=FALSE) +
        theme_bw(base_size=12)+
        theme(axis.title.y=element_blank())+
        ggtitle("On-the-day Cancellations"))
```

### ICU Admission Pressures
```{r}
plot_max_attribs<-filter(`summary_max_attribs`,grepl("ICU Admissions delayed 12hr",key))
#plot_max_attribs$key<-with(plot_max_attribs,reorder(key)) 
print(ggplot(plot_max_attribs,aes(x=Scenario,y=value,fill=Scenario)) +
        geom_boxplot(show.legend=FALSE) +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6,show.legend=FALSE) +
        theme_bw(base_size=12)+
        theme(axis.title.y=element_blank())+
        ggtitle("ICU Admissions delayed 12hrs"))
```

### Wd21 Admission Pressures
```{r}
plot_max_attribs<-filter(`summary_max_attribs`,grepl("Wd21 Admissions delayed 12hr",key))
#plot_max_attribs$key<-with(plot_max_attribs,reorder(key)) 
print(ggplot(plot_max_attribs,aes(x=Scenario,y=value,fill=Scenario)) +
        geom_boxplot(show.legend=FALSE) +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6,show.legend=FALSE) +
        theme_bw(base_size=12)+
        theme(axis.title.y=element_blank())+
        ggtitle("Wd21 Admissions delayed 12hrs"))
```

### Critical Care Discharge Pressures
nb includes Wd21 monitored beds and Periop unit


```{r}
plot_max_attribs<-filter(`summary_max_attribs`,grepl("Ward Discharges delayed 24hr",key))
#plot_max_attribs$key<-with(plot_max_attribs,reorder(key)) 
print(ggplot(plot_max_attribs,aes(x=Scenario,y=value,fill=Scenario)) +
        geom_boxplot(show.legend=FALSE) +
        stat_summary(fun.y=mean, geom="point", shape=23,size=6,show.legend=FALSE) +
        theme_bw(base_size=12)+
        theme(axis.title.y=element_blank())+
        ggtitle("Critical Care Discharges delayed 24hrs"))
```